### 2008-09-02 doc/storage_system/arc1-storage-documentation.tex
renaming httpd --> hopi

The Shepherd could communicate with the file transfer services via backend modules. Currently there are two kinds of backend modules, one for the \emph{byteio} service (which is a simple implementation of a subset of the ByteIO interface) and one for the \emph{httpd} service (which is a simple HED-based HTTP server).

@@

Let's see the scenario for the httpd service which should be in a special `slave' mode for this kind of operation: if a client asks for a file called \verb!file1!, and this file is in the store directory (\verb!./store/file!), then the Shepherd service creates a hardlink into the transfer directory (e.g.~\verb!./transfer/abc!) and sets this file read-only. If the httpd service is configured that way that it handles the HTTP path \verb!/prb! and it is serving files from the directory \verb!./transfer! then after the hardlink is created, we have this URL for this file: \verb!http://localhost:60000/prb/abc!. Now we can give this URL to the client. Then the client \verb!GET!s this URL and gets the file. The httpd service removes (unlinks) this file immediately after the \verb!GET! request arrived, which makes this \verb!http://localhost:60000/prb/abc! URL invalid (so this is a one-time URL), but because of the hardlink the file is still there in the store directory, it is just removed from the transfer directory. Now if some other user wants this file, the Shepherd creates an other hardlink, e.g.~\verb!./transfer/qwe! and now we have an URL \verb!http://localhost:60000/prb/qwe!.

If a client wants to upload a new file, then the Shepherd creates an empty file in the store directory, e.g.~\verb!./store/file2! and creates a hardlink into the transfer directory, e.g.~\verb!./transfer/oiu! and makes it writable, and now we have a URL \verb!http://localhost:60000/prb/oiu!, and the client is able to do a \verb!PUT! to this URL. When the client \verb!PUT!s the file there, the httpd service immediately removes the uploaded file from the transfer directory, but because it has a hardlink in the store directory, the file is stored there as \verb!./store/file2!. The backend module for the httpd service periodically checks whether a new file has two or just one hard links. If it has only one that means that a file is uploaded, so it could notify the Shepherd that the file is arrived. In order to do that, all the backend modules get a callback method `file\_arrived' from the Shepherd.

@@

\begin{verbatim}
$ cat testfile 
This is a testfile.
$ arc_storage_cli put testfile /tmp/
- The size of the file is 20 bytes
- The md5 checksum of the file is 9a9dffa22d227afe0f1959f936993a80
- ARC_BARTENDER_URL environment variable not found, using http://localhost:60000/Bartender
- Calling the Bartender's putFile method...
- done in 0.08 seconds.
- Got transfer URL: http://localhost:60000/httpd/d15900f5-34ee-4bba-bb10-73d60d1c0d75
- Uploading from 'testfile'
    to 'http://localhost:60000/httpd/d15900f5-34ee-4bba-bb10-73d60d1c0d75' with http...
Uploading 20 bytes... data sent, waiting... done.
- done in 0.0042 seconds.
'testfile' (20 bytes) uploaded as '/tmp/testfile'.
$ arc_storage_cli stat /tmp/testfile
- ARC_BARTENDER_URL environment variable not found, using http://localhost:60000/Bartender
- Calling the Bartender's stat method...
- done in 0.05 seconds.
'/tmp/testfile': found
  states
    checksumType: md5
    neededReplicas: 1
    size: 20
    checksum: 9a9dffa22d227afe0f1959f936993a80
  timestamps
    created: 1210232135.57
  parents
    51e12fab-fd3d-43ec-9bc5-17041da3f0b2/testfile: parent
  locations
    http://localhost:60000/Shepherd fc0d3d99-6406-4c43-b2eb-c7ec6d6ab7fe: alive
  entry
    type: file
$ arc_storage_cli get /tmp/testfile newfile
- ARC_BARTENDER_URL environment variable not found, using http://localhost:60000/Bartender
- Calling the Bartender's getFile method...
- done in 0.05 seconds.
- Got transfer URL: http://localhost:60000/httpd/dab911d0-110f-468e-b0c3-627af6e3af31
- Downloading from 'http://localhost:60000/httpd/dab911d0-110f-468e-b0c3-627af6e3af31'
    to 'newfile' with http...
Downloading 20 bytes... done.
- done in 0.0035 seconds.
'/tmp/testfile' (20 bytes) downloaded as 'newfile'.
$ cat newfile 
This is a testfile.
\end{verbatim}

>>>>

The Shepherd could communicate with the file transfer services via backend modules. Currently there are two kinds of backend modules, one for the \emph{byteio} service (which is a simple implementation of a subset of the ByteIO interface) and one for the \emph{hopi} service (which is a simple HED-based HTTP server).

@@

Let's see the scenario for the hopi service which should be in a special `slave' mode for this kind of operation: if a client asks for a file called \verb!file1!, and this file is in the store directory (\verb!./store/file!), then the Shepherd service creates a hardlink into the transfer directory (e.g.~\verb!./transfer/abc!) and sets this file read-only. If the hopi service is configured that way that it handles the HTTP path \verb!/prb! and it is serving files from the directory \verb!./transfer! then after the hardlink is created, we have this URL for this file: \verb!http://localhost:60000/prb/abc!. Now we can give this URL to the client. Then the client \verb!GET!s this URL and gets the file. The hopi service removes (unlinks) this file immediately after the \verb!GET! request arrived, which makes this \verb!http://localhost:60000/prb/abc! URL invalid (so this is a one-time URL), but because of the hardlink the file is still there in the store directory, it is just removed from the transfer directory. Now if some other user wants this file, the Shepherd creates an other hardlink, e.g.~\verb!./transfer/qwe! and now we have an URL \verb!http://localhost:60000/prb/qwe!.

If a client wants to upload a new file, then the Shepherd creates an empty file in the store directory, e.g.~\verb!./store/file2! and creates a hardlink into the transfer directory, e.g.~\verb!./transfer/oiu! and makes it writable, and now we have a URL \verb!http://localhost:60000/prb/oiu!, and the client is able to do a \verb!PUT! to this URL. When the client \verb!PUT!s the file there, the hopi service immediately removes the uploaded file from the transfer directory, but because it has a hardlink in the store directory, the file is stored there as \verb!./store/file2!. The backend module for the hopi service periodically checks whether a new file has two or just one hard links. If it has only one that means that a file is uploaded, so it could notify the Shepherd that the file is arrived. In order to do that, all the backend modules get a callback method `file\_arrived' from the Shepherd.

@@

\begin{verbatim}
$ cat testfile 
This is a testfile.
$ arc_storage_cli put testfile /tmp/
- The size of the file is 20 bytes
- The md5 checksum of the file is 9a9dffa22d227afe0f1959f936993a80
- ARC_BARTENDER_URL environment variable not found, using http://localhost:60000/Bartender
- Calling the Bartender's putFile method...
- done in 0.08 seconds.
- Got transfer URL: http://localhost:60000/hopi/d15900f5-34ee-4bba-bb10-73d60d1c0d75
- Uploading from 'testfile'
    to 'http://localhost:60000/hopi/d15900f5-34ee-4bba-bb10-73d60d1c0d75' with http...
Uploading 20 bytes... data sent, waiting... done.
- done in 0.0042 seconds.
'testfile' (20 bytes) uploaded as '/tmp/testfile'.
$ arc_storage_cli stat /tmp/testfile
- ARC_BARTENDER_URL environment variable not found, using http://localhost:60000/Bartender
- Calling the Bartender's stat method...
- done in 0.05 seconds.
'/tmp/testfile': found
  states
    checksumType: md5
    neededReplicas: 1
    size: 20
    checksum: 9a9dffa22d227afe0f1959f936993a80
  timestamps
    created: 1210232135.57
  parents
    51e12fab-fd3d-43ec-9bc5-17041da3f0b2/testfile: parent
  locations
    http://localhost:60000/Shepherd fc0d3d99-6406-4c43-b2eb-c7ec6d6ab7fe: alive
  entry
    type: file
$ arc_storage_cli get /tmp/testfile newfile
- ARC_BARTENDER_URL environment variable not found, using http://localhost:60000/Bartender
- Calling the Bartender's getFile method...
- done in 0.05 seconds.
- Got transfer URL: http://localhost:60000/hopi/dab911d0-110f-468e-b0c3-627af6e3af31
- Downloading from 'http://localhost:60000/hopi/dab911d0-110f-468e-b0c3-627af6e3af31'
    to 'newfile' with http...
Downloading 20 bytes... done.
- done in 0.0035 seconds.
'/tmp/testfile' (20 bytes) downloaded as 'newfile'.
$ cat newfile 
This is a testfile.
\end{verbatim}
